---
title: What Am I Doing?
author: Scott Sabol
date: '2020-06-10'
tags:
  - blog
  - R
  - ggplot2
  - Rmarkdown
slug: first-post
---

I have no idea why I have started this, well, I guess blog.  I've toyed around with the idea that it could be something where I put information that I learn and need one spot to keep it all.  I think I'll go with that.  

R programming language has also been something that I have been learning/writing in for a little while now.  Ggplot2 has been a package that has been fascinating to me and learning about graphics and design is something that fills my nerdy tech bucket.  I think this first post and a series of posts will be notes, exercises, and other thoughts as I go through the [ggplot2 book](https://ggplot2-book.org/) by Hadley Wickham.

Oh, I have no idea how to use RMarkdown, so I guess this blog will be my trial by fire.  

# Chapter 1

Chapter 1 introduces the Grammar of Graphics concept.

* **Data** and their aesthetic **mapping**.
* **Layers** comprised of **geoms** and **stats**
* **Scales** map values in the data space to values in an aesthetic space
* **Coord** is short for the coordinate system
* **Facet**ing to break up the data into subsets
* **Theme** to control the finer points or details.

#Chapter 2

So chapter 2 jumps right in to creating graphs using the mpg dataset.  I'll jump into the exercises in this first part as there isn't too much detail right off the bat.

## Section 2.2  
### 2.2.1 Exercises (I'll be jumping around a bit)

Question 3  
Convert mpg to European standard l/100km.
```{r message = FALSE}
library(ggplot2)
library(dplyr)
```
```{r}
mpg %>% 
  mutate(cty_l_per_100km = (1 / (cty * (1 / 62) * (1 / 3.78541))),
         hwy_l_per_100km = (1 / (hwy * (1 / 62) * (1 / 3.78541)))) %>% 
  select(cty, cty_l_per_100km, hwy, hwy_l_per_100km)

```
Question 4  
Which manufacturer has the most models?
```{r}
mpg %>% 
  distinct(manufacturer, model) %>% 
  group_by(manufacturer) %>% 
  tally() %>% 
  arrange(desc(n))
```

Which model has the most variants?
```{r}
mpg %>% 
  group_by(model) %>% 
  tally() %>% 
  arrange(desc(n))
```
## Section 2.3

3 key components of every ggplot2 plot:

 - data
 - aesthetic mappings
 - geom function

### 2.3.1 Exercises

Question 2

```{r}
ggplot(mpg, aes(model, manufacturer)) + geom_point()
```
Point geom not useful on two qualitative variables.

Question 3
```{r}
ggplot(mpg, aes(cty, hwy)) + geom_point()
```
```{r}
ggplot(diamonds, aes(carat, price)) + geom_point()
```
```{r}
ggplot(economics, aes(date, unemploy)) + geom_line()
```
```{r message = FALSE}
ggplot(mpg, aes(cty)) + geom_histogram()
```


 

